### 2022-04-20 greta/hopf_mcmc.Rmd

```{r}
library(tidyverse)
library(greta)
library(bayesplot)

set.seed(4242)
train_reps <- 10
train_t_max <- 100
test_t_max <- 100
test_reps <- 100

@@

```{r}
#test_reps <- 100
## draw test_reps number of samples
left_off <- train |> 
  filter(t == train_t_max) |> 
  select(H,P) |> 
  rename(H_init = H, P_init = P) |>
  slice_sample(n = test_reps, replace=TRUE)

@@

```{r}
bind_rows(mutate(train, type="training"), 
          mutate(test,type="observed"),  
          mutate(posterior_sims, type="predicted")) |>
  rename("host" = H, "parasite" = P) |>
pivot_longer(c(host, parasite), values_to="density", names_to="species") |>
  ggplot(aes(t, density, col=type, group=interaction(i,type))) + geom_line(alpha=0.2) +
  geom_vline(aes(xintercept = train_t_max)) + facet_wrap(~species, ncol=1)
```

@@

First, a single 'observed' sample from the true:

@@

}
# ensemble predictions
dat <- 
  posterior_sims |> 
  pivot_wider(id_cols = "t", names_from="i", values_from = "P") |> 
  select(-t) |> as.matrix()

```
```{r}
# score over all replicates:
bench::bench_time({
rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$P, dat)) |> 
  bind_rows()
})
```

```{r}
rep_scores |> summarise(across(.fns= base::mean))

library(patchwork)
ggplot(rep_scores) + geom_histogram(aes(crps)) + 
(ggplot(rep_scores) + geom_histogram(aes(logs)) )

@@

>>>>

```{r message=FALSE}
library(tidyverse, quietly = TRUE)
library(greta, quietly = TRUE)
library(bayesplot, quietly = TRUE)
```

```{r}
set.seed(4242)
train_reps <- 1
train_t_max <- 100
test_t_max <- 100
test_reps <- train_reps # same as train_reps since test cases are continuations of the training rep time series

@@

```{r}
test_reps <- 100
## draw test_reps number of samples
left_off <- train |> 
  filter(t == train_t_max) |> 
  select(H,P) |> 
  rename(H_init = H, P_init = P) |>
  slice_sample(n = test_reps, replace=TRUE)

@@

```{r}
combined <- 
  bind_rows(
    mutate(train, type="training"), 
    mutate(test,type="observed"),  
    mutate(posterior_sims, type="predicted") |> filter(i %in% 1:3)
    ) |>
  rename("host" = H, "parasite" = P) |>
  pivot_longer(c(host, parasite), values_to="density", names_to="species")

combined |> 
  ggplot(aes(t, density, col=type, group=interaction(i,type))) + 
  geom_line(alpha=0.5) +
  geom_vline(aes(xintercept = train_t_max)) + facet_wrap(~species, ncol=1)
```

@@

@@

}
```

We score predictions of each variable seperately.  First the predator (Parasite):

```{r}
# ensemble predictions
P_dat <- 
  posterior_sims |> 
  pivot_wider(id_cols = "t", names_from="i", values_from = "P") |> 
  select(-t) |> as.matrix()

@@

```{r}
# score over all replicates:

rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$P, P_dat)) |> 
  bind_rows()

rep_scores |> summarise(across(.fns= base::mean))
